---
title: "Mark Appel Pitch Report"
output:
  html_document:
    css: styles.css
---

```{r setup, include=FALSE}
library(reshape)
library(rlang)
library(tidyverse)
library(mgcv)
library(REdaS)
library(gridExtra)
library(lme4)
library(Hmisc)
library(gt)
library(glue)
library(cowplot)
library(merTools)
library(flextable)
options(scipen = 999)
memory.limit(100000)

minors2019 <- read.csv("minors_2021.csv")
all_pitches <- readRDS("all_pitches.rds")
all_2020 <- readRDS("all_2020.rds")
overall <- readRDS("overall.rds")

all_pitches_all <- rbind(all_pitches,all_2020)

all_pitches_all <-mutate(all_pitches_all, whiff=ifelse(description %in% c("swinging_strike","swinging_strike_blocked"),
                                                           1, 0))

all_pitches_all <- all_pitches_all[,c("pitcher",
                              "player_name",
                              "pitch_type",
                              "Season",
                              "p_throws",
                              "stand",
                              "release_speed",
                              "release_pos_x",
                              "release_pos_z",
                              "plate_x",
                              "plate_z",
                              "pfx_x",
                              "pfx_z",
                              "vx0",
                              "vy0",
                              "vz0",
                              "ax",
                              "ay",
                              "az",
                              "release_spin_rate",
                              "release_extension",
                              "whiff",
                              "barrel")]

all_pitches_all <- distinct(all_pitches_all)

pitch_stats <- all_pitches_all %>%
  group_by(pitcher, player_name, pitch_type,p_throws) %>% 
  arrange(pitcher, player_name, pitch_type,p_throws) %>%
  summarise(Pitches = n(),
            Velocity = round(mean(release_speed,na.rm=TRUE),1),
            Release_x = round(mean(release_pos_x,na.rm=TRUE),2),
            Release_z = round(mean(release_pos_z,na.rm=TRUE),2),
            pfx_x = round(mean(pfx_x,na.rm=TRUE),2),
            pfx_z = round(mean(pfx_z,na.rm=TRUE),2),
            vx0 = round(mean(vx0,na.rm=TRUE),2),
            vy0 = round(mean(vy0,na.rm=TRUE),2),
            vz0 = round(mean(vz0,na.rm=TRUE),2),
            ax = round(mean(ax,na.rm=TRUE),2),
            ay = round(mean(ay,na.rm=TRUE),2),
            az = round(mean(az,na.rm=TRUE),2),
            release_spin_rate = round(mean(release_spin_rate,na.rm=TRUE),1),
            release_extension = round(mean(release_extension,na.rm=TRUE),1),
            Whiff = round(mean(whiff,na.rm=TRUE),3),
            Barrel = round(mean(barrel,na.rm=TRUE),3),
            .groups = 'drop') %>%
  filter(Pitches >= 50)

pitch_stats <- mutate(pitch_stats, pitch_group=ifelse(pitch_type %in% c("FF", "FT","FC", "SI", "FA"),
                                                              "Fastball", ifelse(pitch_type %in% c("SL", "EP","CU", "KN", "KC"),
                                                                                 "Breaking", "OffSpeed")))

pitch_stats$pfx_x <- pitch_stats$pfx_x * -12
pitch_stats$pfx_z <- pitch_stats$pfx_z * 12
pitch_stats$Move_Angle <- round(rad2deg(atan2(pitch_stats$pfx_x,pitch_stats$pfx_z)),1)
pitch_stats$Move_Angle <- (pitch_stats$Move_Angle + 360) %% 360

pitch_stats <- pitch_stats %>%
  filter(!is.na(Velocity)) %>%
  filter(!is.na(release_extension)) %>%
  filter(!is.na(Release_z)) %>%
  filter(!is.na(pfx_x)) %>%
  filter(!is.na(pfx_z))

pitch_stats <- left_join(pitch_stats,overall)

pitch_stats <- pitch_stats %>%
  filter(!is.na(xRV_plus))

pitch_comps <- function(pitch_type, velo, release_extend, release_height, hmove, vmove)
{
  
  if(pitch_type %in% c("FF", "FT","FC", "SI", "FA"))
   {
     sample <- pitch_stats %>%
      filter(pitch_group == "Fastball")

     Dist <- mahalanobis(x = sample[,c("Velocity","release_extension","Release_z","pfx_x","pfx_z")], c(velo,release_extend,release_height,hmove,vmove), cov(sample[,c("Velocity","release_extension","Release_z","pfx_x","pfx_z")]))
     sample$Dist <- Dist
     sample$Dist <- round(sample$Dist,3)
     sample <- sample[order(sample$Dist, decreasing=FALSE),]
  }
  else if(pitch_type %in% c("SL", "EP","CU", "KN", "KC"))
  {
    sample <- pitch_stats %>%
      filter(pitch_group == "Breaking")
    
    Dist <- mahalanobis(x = sample[,c("pfx_x","pfx_z")], c(hmove,vmove), cov(sample[,c("pfx_x","pfx_z")]))
    sample$Dist <- Dist
    sample$Dist <- round(sample$Dist,3)
    sample <- sample[order(sample$Dist, decreasing=FALSE),]
  }
  else
  {
    sample <- pitch_stats %>%
      filter(pitch_group == "OffSpeed")
    
    Dist <- mahalanobis(x = sample[,c("pfx_x","pfx_z")], c(hmove,vmove), cov(sample[,c("pfx_x","pfx_z")]))
    sample$Dist <- Dist
    sample$Dist <- round(sample$Dist,3)
    sample <- sample[order(sample$Dist, decreasing=FALSE),]
  }
}

create_stat_report <- function(pitcher)
{
stats <- minors2019 %>%
  filter(Name == pitcher)

table <- data.frame(t(stats[,c("IP","H","SO","BB","W","SV","ERA")]))
table <- cbind(names = row.names(table),table)
colnames(table) <- c("names","stats")


stats_summary <- gt(table,groupname_col = "names")  %>%
  tab_header(
    title = glue('{pitcher}'),
    subtitle = "2021 MiLB Stats") %>%
  tab_options(table.width = pct(50),
              heading.title.font.weight = "bold",
              heading.title.font.size = pct(300)) %>%
  tab_options(
    heading.background.color = "#44b4e1") %>%
  tab_style(style = list(
    cell_fill(color = "#35316a"),
    cell_text(weight = "bold", color = "white")
  ),
  locations = cells_row_groups(groups = unique(table$names))) %>%
  cols_label(
    stats = "") %>%
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  fmt_number(
    columns = "stats",
    rows = c(2,3,4,5,6),
    decimals = 0)%>%
  fmt_number(
    columns = "stats",
    rows = c(1),
    decimals = 1)%>%
  fmt_number(
    columns = "stats",
    rows = c(7),
    decimals = 2)
stats_summary
}

pitch_locations <- function(pitch, velo, release_extend, release_height, hmove, vmove)
{
  if(pitch %in% c("FF", "FT","FC", "SI", "FA"))
    {
      sample <- all_pitches_all %>%
        filter(pitch_type %in% c("FF", "FT","FC", "SI", "FA")) %>%
        filter(!is.na(release_speed))%>%
        filter(!is.na(release_extension))%>%
        filter(!is.na(release_pos_z))%>%
        filter(!is.na(pfx_x))%>%
        filter(!is.na(pfx_z))
      
      sample$pfx_x <- sample$pfx_x * -12
      sample$pfx_z <- sample$pfx_z * 12
      
      Dist <- mahalanobis(x = sample[,c("release_speed","release_extension","release_pos_z","pfx_x","pfx_z")], c(velo,release_extend,release_height,hmove,vmove), cov(sample[,c("release_speed","release_extension","release_pos_z","pfx_x","pfx_z")]))
      sample$Dist <- Dist
      sample$Dist <- round(sample$Dist,3)
      sample <- sample[order(sample$Dist, decreasing=FALSE),]
    }
    else if(pitch %in% c("SL", "EP","CU", "KN", "KC"))
    {
      sample <- all_pitches_all %>%
        filter(pitch_type %in% c("SL", "EP","CU", "KN", "KC")) %>%
        filter(!is.na(release_speed))%>%
        filter(!is.na(release_extension))%>%
        filter(!is.na(release_pos_z))%>%
        filter(!is.na(pfx_x))%>%
        filter(!is.na(pfx_z))
      
      sample$pfx_x <- sample$pfx_x * -12
      sample$pfx_z <- sample$pfx_z * 12
      
      Dist <- mahalanobis(x = sample[,c("pfx_x","pfx_z")], c(hmove,vmove), cov(sample[,c("pfx_x","pfx_z")]))
      sample$Dist <- Dist
      sample$Dist <- round(sample$Dist,3)
      sample <- sample[order(sample$Dist, decreasing=FALSE),]
    }
    else
    {
      sample <- all_pitches_all %>%
        filter(pitch_type %in% c("CH","CS","FO", "FS")) %>%
        filter(!is.na(release_speed))%>%
        filter(!is.na(release_extension))%>%
        filter(!is.na(release_pos_z))%>%
        filter(!is.na(pfx_x))%>%
        filter(!is.na(pfx_z))
      
      sample$pfx_x <- sample$pfx_x * -12
      sample$pfx_z <- sample$pfx_z * 12
      
      Dist <- mahalanobis(x = sample[,c("pfx_x","pfx_z")], c(hmove,vmove), cov(sample[,c("pfx_x","pfx_z")]))
      sample$Dist <- Dist
      sample$Dist <- round(sample$Dist,3)
      sample <- sample[order(sample$Dist, decreasing=FALSE),]
    }
  sample_bip <- sample %>%
    filter(!is.na(barrel))
  sample_bip <- sample_bip[1:500,]
  sample <- sample[1:1000,]
  
  topKzone <- 3.5
  botKzone <- 1.6
  inKzone <- -0.95
  outKzone <- 0.95
  kZone <- data.frame(
    x=c(inKzone, inKzone, outKzone, outKzone, inKzone),
    y=c(botKzone, topKzone, topKzone, botKzone, botKzone)
  )

  fit <- gam(whiff ~ s(plate_x,plate_z), family=binomial, data=sample)
  plate_x <- seq(-1.5, 1.5, length.out=100)
  plate_z <- seq(1, 4, length.out=100)
  data.predict <- data.frame(plate_x = c(outer(plate_x, plate_z * 0 + 1)),
                             plate_z = c(outer(plate_x * 0 + 1, plate_z)))
  lp <- predict(fit, data.predict)
  data.predict$Probability <- exp(lp) / (1 + exp(lp))
  
  # construct the plot V Oppo
  whiff <- ggplot(kZone, aes(x, y)) +
    theme_void() +
    geom_tile(data=data.predict, 
              aes(x=-plate_x, y=plate_z, fill= Probability)) +
    scale_fill_distiller(palette = "Spectral") +
    geom_path(lwd=1, col="black") +
    coord_fixed()+labs(title="Whiffs")
  
  fit <- gam(barrel ~ s(plate_x,plate_z), family=binomial, data=sample_bip)
  plate_x <- seq(-1.5, 1.5, length.out=100)
  plate_z <- seq(1, 4, length.out=100)
  data.predict <- data.frame(plate_x = c(outer(plate_x, plate_z * 0 + 1)),
                             plate_z = c(outer(plate_x * 0 + 1, plate_z)))
  lp <- predict(fit, data.predict)
  data.predict$Probability <- exp(lp) / (1 + exp(lp))
  
  # construct the plot V Oppo
  barrel <- ggplot(kZone, aes(x, y)) +
    theme_void() +
    geom_tile(data=data.predict, 
              aes(x=-plate_x, y=plate_z, fill= Probability)) +
    scale_fill_distiller(palette = "Spectral") +
    geom_path(lwd=1, col="black") +
    coord_fixed()+labs(title="Barrels")
  
  grid.arrange(
    whiff,
    barrel,
    nrow = 1,
    top = "",
    bottom = ""
  )
}


pitch_locations_value <- function(pitch, velo, release_extend, release_height, hmove, vmove, handedness)
{
  if(pitch %in% c("FF", "FT","FC", "SI", "FA"))
  {
    sample <- all_pitches_all %>%
      filter(pitch_type %in% c("FF", "FT","FC", "SI", "FA")) %>%
      filter(!is.na(release_speed))%>%
      filter(!is.na(release_extension))%>%
      filter(!is.na(release_pos_z))%>%
      filter(!is.na(pfx_x))%>%
      filter(!is.na(pfx_z))
    
    sample$pfx_x <- sample$pfx_x * -12
    sample$pfx_z <- sample$pfx_z * 12
    
    if(handedness == "R")
    {
      sample <- sample %>%
        filter(stand == "R")
    }
    else
    {
      sample <- sample %>%
        filter(stand == "L") 
    }
    
    Dist <- mahalanobis(x = sample[,c("release_speed","release_extension","release_pos_z","pfx_x","pfx_z")], c(velo,release_extend,release_height,hmove,vmove), cov(sample[,c("release_speed","release_extension","release_pos_z","pfx_x","pfx_z")]))
    sample$Dist <- Dist
    sample$Dist <- round(sample$Dist,3)
    sample <- sample[order(sample$Dist, decreasing=FALSE),]
  }
  else if(pitch %in% c("SL", "EP","CU", "KN", "KC"))
  {
    sample <- all_pitches_all %>%
      filter(pitch_type %in% c("SL", "EP","CU", "KN", "KC")) %>%
      filter(!is.na(release_speed))%>%
      filter(!is.na(release_extension))%>%
      filter(!is.na(release_pos_z))%>%
      filter(!is.na(pfx_x))%>%
      filter(!is.na(pfx_z))
    
    sample$pfx_x <- sample$pfx_x * -12
    sample$pfx_z <- sample$pfx_z * 12
    
    if(handedness == "R")
    {
      sample <- sample %>%
        filter(stand == "R")
    }
    else
    {
      sample <- sample %>%
        filter(stand == "L") 
    }
    
    Dist <- mahalanobis(x = sample[,c("pfx_x","pfx_z")], c(hmove,vmove), cov(sample[,c("pfx_x","pfx_z")]))
    sample$Dist <- Dist
    sample$Dist <- round(sample$Dist,3)
    sample <- sample[order(sample$Dist, decreasing=FALSE),]
  }
  else
  {
    sample <- all_pitches_all %>%
      filter(pitch_type %in% c("CH","CS","FO", "FS")) %>%
      filter(!is.na(release_speed))%>%
      filter(!is.na(release_extension))%>%
      filter(!is.na(release_pos_z))%>%
      filter(!is.na(pfx_x))%>%
      filter(!is.na(pfx_z))
    
    sample$pfx_x <- sample$pfx_x * -12
    sample$pfx_z <- sample$pfx_z * 12
    
    if(handedness == "R")
    {
      sample <- sample %>%
        filter(stand == "R")
    }
    else
    {
      sample <- sample %>%
        filter(stand == "L") 
    }
    
    Dist <- mahalanobis(x = sample[,c("pfx_x","pfx_z")], c(hmove,vmove), cov(sample[,c("pfx_x","pfx_z")]))
    sample$Dist <- Dist
    sample$Dist <- round(sample$Dist,3)
    sample <- sample[order(sample$Dist, decreasing=FALSE),]
  }
  sample_bip <- sample %>%
    filter(!is.na(barrel))
  sample_bip <- sample_bip[1:500,]
  sample <- sample[1:1000,]
  
  topKzone <- 3.5
  botKzone <- 1.6
  inKzone <- -0.95
  outKzone <- 0.95
  kZone <- data.frame(
    x=c(inKzone, inKzone, outKzone, outKzone, inKzone),
    y=c(botKzone, topKzone, topKzone, botKzone, botKzone)
  )
  
  fit <- gam(whiff ~ s(plate_x,plate_z), family=binomial, data=sample)
  plate_x <- seq(-1.5, 1.5, length.out=100)
  plate_z <- seq(1, 4, length.out=100)
  data.predict_whiff <- data.frame(plate_x = c(outer(plate_x, plate_z * 0 + 1)),
                             plate_z = c(outer(plate_x * 0 + 1, plate_z)))
  lp <- predict(fit, data.predict_whiff)
  data.predict_whiff$Whiff <- exp(lp) / (1 + exp(lp))
  
  
  fit <- gam(barrel ~ s(plate_x,plate_z), family=binomial, data=sample_bip)
  plate_x <- seq(-1.5, 1.5, length.out=100)
  plate_z <- seq(1, 4, length.out=100)
  data.predict_barrel <- data.frame(plate_x = c(outer(plate_x, plate_z * 0 + 1)),
                             plate_z = c(outer(plate_x * 0 + 1, plate_z)))
  lp <- predict(fit, data.predict_barrel)
  data.predict_barrel$Barrel <- exp(lp) / (1 + exp(lp))
  
  data.predict <- left_join(data.predict_whiff,data.predict_barrel)
  data.predict$Value <- data.predict$Whiff - data.predict$Barrel
  
  # construct the plot V Oppo
  ggplot(kZone, aes(x, y)) +
    theme_void() +
    geom_tile(data=data.predict, 
              aes(x=-plate_x, y=plate_z, fill= Value),show.legend = FALSE) +
    scale_fill_gradient2(low = "red",mid = "white", high = "green") +
    geom_path(lwd=1, col="black") +
    coord_fixed()+labs(title="Location Value") +
    geom_contour(data=data.predict,
                 aes(x=-plate_x, y=plate_z,z = Value)
                 ,breaks = .1, colour = "darkgreen") +
    geom_contour(data=data.predict,
                 aes(x=-plate_x, y=plate_z,z = Value)
                 ,breaks = -0.05, colour = "darkred")
  
  
}
    
```

# 2021 Stats and Pitch Characteristics
&nbsp;
&nbsp;
```{r stats, echo = FALSE, warning=FALSE}
create_stat_report("Mark Appel")

pitches <- data.frame('Pitch_Type' = c("FF","SL","CH"),
                      "Velocity" = c(92.4,81.4,85.8),
                      "Release_Extension" = c(6.92,6.63,6.66),
                      "Release_Height" = c(round(72.8/12,2),round(71.2/12,2),round(70.6/12,2)),
                      "Horizontal_Movement" = c(12.8,-0.42,13.52),
                      "Vertical_Movement" = c(12.88,-1.73,7.59)
)
```
<br>
<center>
<video width="640" height="480" controls>
  <source src="appelpunchouts.mp4" type="video/mp4">
</video>
</center>
<br>
```{r characteristics, echo = FALSE, warning=FALSE}
gt(pitches)  %>%
        tab_header(
            title = "Pitch Summary",
            subtitle = md("&nbsp;")) %>%
    tab_options(
    heading.background.color = "#44b4e1",
    column_labels.background.color = "#35316a",
    heading.title.font.weight = "bold",
              heading.title.font.size = pct(200))  %>%
        cols_label(
          Pitch_Type = "Pitch Type",
          Release_Extension = "Release Extension",
          Release_Height = "Release Height",
          Horizontal_Movement = "Horizontal Movement",
          Vertical_Movement = "Vertical Movement"
        )

```
------

## Mechanics Side View Progression

<center>
<video width="640" height="480" controls>
  <source src="appelside.mp4" type="video/mp4">
</video>
</center>
<br>

## Mechanics Front View Progression

<center>
<video width="640" height="480" controls>
  <source src="appelfront.mp4" type="video/mp4">
</video>
</center>
<br>

------

# Pitch Comps
Using data since 2015, we were able to generate a list of the most similar pitches to your pitches as they currently stand based on a number of different factors. These include:

* Velocity
* Release Extension
* Release Height
* Movement Profile
<br>

------

### Fastball
&nbsp;
&nbsp;
```{r pitch, echo = FALSE, warning=FALSE}
test <- pitch_comps(pitches[1,"Pitch_Type"],pitches[1,"Velocity"],pitches[1,"Release_Extension"],pitches[1,"Release_Height"],pitches[1,"Horizontal_Movement"],pitches[1,"Vertical_Movement"])

pitch <- data.frame("player_name" = "Mark Appel",
                    "pitch_type" = "FF",
                    "Velocity" = pitches[1,"Velocity"],
                    "release_extension" = pitches[1,"Release_Extension"], 
                    "Release_z" = pitches[1,"Release_Height"]
                    ,"pfx_x" = pitches[1,"Horizontal_Movement"]
                    ,"pfx_z" = pitches[1,"Vertical_Movement"]
                    , "Whiff" = NA
                    ,"Barrel" = NA
                    , "xRV_plus" = NA
                    )

test <- rbind(pitch,test[,c("player_name","pitch_type","Velocity","release_extension","Release_z","pfx_x","pfx_z", "Whiff","Barrel", "xRV_plus")])

gt(test[1:6,c("player_name","pitch_type","Velocity","release_extension","Release_z","pfx_x","pfx_z", "Whiff","Barrel", "xRV_plus")])  %>%
        tab_header(
            title = "Most Similar Pitches",
            subtitle = md("&nbsp;")) %>%
    tab_options(
    heading.background.color = "#44b4e1",
    column_labels.background.color = "#35316a",
    heading.title.font.weight = "bold",
              heading.title.font.size = pct(200)) %>%
        cols_label(
            player_name = "Pitcher",
            pitch_type = "Pitch Type",
            xRV_plus = "xRV+",
            release_extension = "Release Extension",
            Release_z = "Release Height",
            pfx_x = "Horizontal Movement",
            pfx_z = "Vertical Movement"
        ) %>%
  fmt_percent(
    columns = c("Whiff","Barrel"),
    decimals = 1) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightgray"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      rows = 1
    )
  )
```
<br>

* There aren't many pitchers with fastballs similar to yours
<br>
* We need to determine the best route for you to take depending on what feels more comfortable/easier for you
<br>
* Path One: Lean into the sinker and try to add more run onto the pitch (15 H/12 V)
<br>
* Path Two: Throw a high vert rising fastball add more vertical break and try to get less run (10 H/15+ V)

------

### Slider
&nbsp;
&nbsp;

```{r pitch2, echo = FALSE, warning=FALSE}
test <- pitch_comps(pitches[2,"Pitch_Type"],pitches[2,"Velocity"],pitches[2,"Release_Extension"],pitches[2,"Release_Height"],pitches[2,"Horizontal_Movement"],pitches[2,"Vertical_Movement"])

pitch <- data.frame("player_name" = "Mark Appel",
                    "pitch_type" = pitches[2,"Pitch_Type"],
                    "Velocity" = pitches[2,"Velocity"],
                    "release_extension" = pitches[2,"Release_Extension"], 
                    "Release_z" = pitches[2,"Release_Height"]
                    ,"pfx_x" = pitches[2,"Horizontal_Movement"]
                    ,"pfx_z" = pitches[2,"Vertical_Movement"]
                    , "Whiff" = NA
                    ,"Barrel" = NA
                    , "xRV_plus" = NA
                    )


test <- rbind(pitch,test[,c("player_name","pitch_type","Velocity","release_extension","Release_z","pfx_x","pfx_z", "Whiff","Barrel", "xRV_plus")])

gt(test[1:6,c("player_name","pitch_type","Velocity","release_extension","Release_z","pfx_x","pfx_z", "Whiff","Barrel", "xRV_plus")])  %>%
        tab_header(
            title = "Most Similar Pitches",
            subtitle = md("&nbsp;")) %>%
    tab_options(
    heading.background.color = "#44b4e1",
    column_labels.background.color = "#35316a",
    heading.title.font.weight = "bold",
              heading.title.font.size = pct(200)) %>%
        cols_label(
            player_name = "Pitcher",
            pitch_type = "Pitch Type",
            xRV_plus = "xRV+",
            release_extension = "Release Extension",
            Release_z = "Release Height",
            pfx_x = "Horizontal Movement",
            pfx_z = "Vertical Movement"
        ) %>%
  fmt_percent(
    columns = c("Whiff","Barrel"),
    decimals = 1) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightgray"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      rows = 1
    ))
```
<br>

* If we include velocity your slider's best comps are left handed breaking balls
<br>
* First goal for this pitch is to throw it harder
<br>
* Second goal is to add more break - vertical versus horizontal will be determined by fastball approach

------

### Change-Up
&nbsp;
&nbsp;

```{r pitch3, echo = FALSE, warning=FALSE}
test <- pitch_comps(pitches[3,"Pitch_Type"],pitches[3,"Velocity"],pitches[3,"Release_Extension"],pitches[3,"Release_Height"],pitches[3,"Horizontal_Movement"],pitches[3,"Vertical_Movement"])

pitch <- data.frame("player_name" = "Mark Appel",
                    "pitch_type" = pitches[3,"Pitch_Type"],
                    "Velocity" = pitches[3,"Velocity"],
                    "release_extension" = pitches[3,"Release_Extension"], 
                    "Release_z" = pitches[3,"Release_Height"]
                    ,"pfx_x" = pitches[3,"Horizontal_Movement"]
                    ,"pfx_z" = pitches[3,"Vertical_Movement"]
                    , "Whiff" = NA
                    ,"Barrel" = NA
                    , "xRV_plus" = NA
                    )

test <- rbind(pitch,test[,c("player_name","pitch_type","Velocity","release_extension","Release_z","pfx_x","pfx_z", "Whiff","Barrel", "xRV_plus")])

gt(test[1:6,c("player_name","pitch_type","Velocity","release_extension","Release_z","pfx_x","pfx_z", "Whiff","Barrel", "xRV_plus")])  %>%
        tab_header(
            title = "Most Similar Pitches",
            subtitle = md("&nbsp;")) %>%
    tab_options(
    heading.background.color = "#44b4e1",
    column_labels.background.color = "#35316a",
    heading.title.font.weight = "bold",
              heading.title.font.size = pct(200)) %>%
        cols_label(
            player_name = "Pitcher",
            pitch_type = "Pitch Type",
            xRV_plus = "xRV+",
            release_extension = "Release Extension",
            Release_z = "Release Height",
            pfx_x = "Horizontal Movement",
            pfx_z = "Vertical Movement"
        ) %>%
  fmt_percent(
    columns = c("Whiff","Barrel"),
    decimals = 1) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightgray"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      rows = 1
    )
  )
```
<br>

* This actually has the makings of a good pitch we just need to rework a fastball that can build off it
<br>
* Gibson could be a good pitcher type to mirror
<br>
* His main fastball is a sinker that isnt too far from your current fastball

------


## Final Notes

Overall, we will be looking to really determine the path you want to take as a pitcher. We need to decide between a high vert four seam fastball pitcher or a sinker heavy approach. The slider needs to be thrown harder and ideally will add more depth but depending on fastball approach the design of this pitch may change. The change-up has a good design and using Kyle Gibson as a guide it should pair well with a sinking fastball approach.
<br>
Once we are able to generate a pitch profile approach and determine set goals based on what feels comfortable we can generate location charts like the ones below for your current pitches which will help us to find areas to target for success.
<br>
```{r final locations, echo = FALSE, warning=FALSE, message=FALSE}
ff <- pitch_locations_value(pitches[1,"Pitch_Type"],pitches[1,"Velocity"],pitches[1,"Release_Extension"],pitches[1,"Release_Height"],pitches[1,"Horizontal_Movement"],pitches[1,"Vertical_Movement"],"L") +labs(title="Fastball v Left")

sl <- pitch_locations_value(pitches[2,"Pitch_Type"],pitches[2,"Velocity"],pitches[2,"Release_Extension"],pitches[2,"Release_Height"],pitches[2,"Horizontal_Movement"],pitches[2,"Vertical_Movement"], "L") +labs(title="Curve ball v Left")

ch <- pitch_locations_value(pitches[3,"Pitch_Type"],pitches[3,"Velocity"],pitches[3,"Release_Extension"],pitches[3,"Release_Height"],pitches[3,"Horizontal_Movement"],pitches[3,"Vertical_Movement"],"L") +labs(title="Change-up v Left")

ff_r <- pitch_locations_value(pitches[1,"Pitch_Type"],pitches[1,"Velocity"],pitches[1,"Release_Extension"],pitches[1,"Release_Height"],pitches[1,"Horizontal_Movement"],pitches[1,"Vertical_Movement"],"R") +labs(title="Fastball v Right")

Sl_r <- pitch_locations_value(pitches[2,"Pitch_Type"],pitches[2,"Velocity"],pitches[2,"Release_Extension"],pitches[2,"Release_Height"],pitches[2,"Horizontal_Movement"],pitches[2,"Vertical_Movement"], "R") +labs(title="Curve ball v Right")

ch_r <- pitch_locations_value(pitches[3,"Pitch_Type"],pitches[3,"Velocity"],pitches[3,"Release_Extension"],pitches[3,"Release_Height"],pitches[3,"Horizontal_Movement"],pitches[3,"Vertical_Movement"],"R") +labs(title="Change-up v Right")

grid.arrange(
  ff,
  sl,
  ch,
  ff_r,
  Sl_r,
  ch_r,
  nrow = 2,
  top = "",
  bottom = ""
)

```